Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-30 paper/reply.tex
small response editing

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Cristina).}
\end{quote}

@@

4) Proposition 1, item 2, should it be $\hat G$ ?
\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Iury).}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} 
We consider this extension for future work.}
\end{quote}

@@

4) Proposition 1, item 2, should it be $\hat G$ ?
\begin{quote}
\textcolor{blue}{\textbf{Response:} The typo was rectified.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} The parametric errors have same order as the plant because of limitations of DSSynth, further improvements may be done to make it flexible. In fact, we the modeling errors does not depend on sampling, holding and quantization errors, once it already appears in previous continuous time models and are only propagated in the discrete version. The reciprocal is true if the quantization noise is considered exogenous signals as proposed in figures 1 and 2. Although the parametric uncertainties and the sampling and holding process present nonlinearities, our linear approximation is enough to represent the majority of these effects and is usually employed in control systems literature.}
\end{quote}
